### 2016-05-03 config/styles.inc.tex
Some comments from Johan, tom
Remove FRF style
Simplify styles
Improve some figures

%% Colors
  \colorlet{tangored}{TangoScarletRed1}
  \colorlet{tangoblue}{TangoSkyBlue2}
  \colorlet{tangogreen}{TangoChameleon2}
  \colorlet{tangogrey}{TangoAluminium5}

  \colorlet{meas}{TangoPlum2}

@@

  \colorlet{model}{tangogrey}
  \colorlet{bg}{TangoAluminium2}

\colorlet{model}{black}
\colorlet{truesys}{TangoAluminium5}
% \colorlet{truesys}{TangoAluminium4} % from LRMHinf paper

@@

\colorlet{frf}{TangoButter3} %TODO: replace
\colorlet{param}{TangoScarletRed2}

@@

\colorlet{etfe}{TangoButter3}
\colorlet{lrm7111}{TangoPlum3}
\colorlet{lric7222}{TangoChameleon3}
\colorlet{lrm7222}{TangoSkyBlue3}
\colorlet{lrm6222}{TangoOrange3}
\colorlet{lpm744}{TangoScarletRed3}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,opacity=0.75,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
\pgfplotsset{signalhighlight/.style={ycomb,color=signal,solid,line width=1pt,mark=o,mark size=2pt}}

\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
\pgfplotsset{truesys/.style={color=tangogrey,line width=1pt}}
\pgfplotsset{mainsys/.style={color=black,line width=1pt}}
\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}

@@

\pgfplotsset{percentileLines/.style={black,dashed}}
%NOTE: we need tikzset here, these styles are used on NODE (\in TikZ) instead of Pgfplots stuff
\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

@@

%TODO: redefine this thingie for LRM chapters
% \pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}

@@

\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=0.2pt}} %TODO: replace

>>>>

%% Colors
  \colorlet{meas}{TangoPlum2}

@@

  \colorlet{model}{TangoAluminium5}
  \colorlet{bg}{TangoAluminium2}

\colorlet{model}{black}
\colorlet{truesys}{TangoAluminium5}
\colorlet{frf}{truesys}

@@

\colorlet{param}{TangoScarletRed2}

@@

  \colorlet{noisefill}{TangoAluminium1}
  \colorlet{noiseline}{TangoAluminium5}

\colorlet{etfe}{TangoButter3}
\colorlet{lrm7111}{TangoPlum2}
\colorlet{lric7222}{TangoChameleon3}
\colorlet{lrm7222}{TangoSkyBlue3}
\colorlet{lrm6222}{TangoSkyBlue1}
\colorlet{lpm744}{TangoScarletRed3}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,opacity=0.75,area legend}}
\pgfplotsset{noiselevel/.style={fill=noisefill,draw=noiseline,opacity=0.75,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
\pgfplotsset{signalhighlight/.style={ycomb,color=signal,solid,line width=1pt,mark=o,mark size=2pt}}

\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
\pgfplotsset{truesys/.style={color=truesys,line width=1pt}}
\pgfplotsset{mainsys/.style={color=black,line width=1pt}}
\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}

@@

\pgfplotsset{percentileLines/.style={black,dashed}}
%NOTE: we need tikzset here, these styles are used on NODE (\in TikZ) instead of Pgfplots stuff
\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}
\tikzset{trace/.style={align=left,font=\scriptsize,fill opacity=0.8,fill=#1}}
\tikzset{trace/.default=white}

@@

% \pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}
\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=0.2pt}}

@@
